Smart Model Elimination for Efficient Automated Machine Learning in Healthcare

### 2024-06-27 paper/paper.tex
Update paper.tex

Machine learning (ML) algorithms require complicated processes like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning. These frameworks automate the complicated processes of producing effective ML models, making it more accessable to non-experts. To do this on a larger scale and at greater speeds, recent research and effort have been put into developing AutoML frameworks. These frameworks create comfortable environments in which models can excel. They handle missing values, preprocess data, and optimize training to ensure the best results [1].

>>>>

Machine learning (ML) algorithms require complicated processes like hyperparamater tuning, and can be modified in conjunction with one another, like in ensemble learning. AutoML frameworks automate the complicated processes of producing effective ML models, making it more accessable to non-experts. These frameworks create comfortable environments in which models can excel. They handle missing values, preprocess data, and optimize training to ensure the best results [1].
